Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-31 mr-review-outline.Rmd
switched outline to md output format

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
output: 
  - bookdown::html_document2
  - bookdown::word_document2
---

>>>>

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
output: 
  - bookdown::github_document2
  - bookdown::html_document2
  - bookdown::word_document2
---
